---
title: "ASU SCCJ Faculty Salaries 2018-2022"
output: 
  flexdashboard::flex_dashboard:
    theme: yeti
    source: embed
    smart: false
runtime: shiny
---


```{r setup, include = FALSE}

# clear workspace
rm( list = ls() )

# load the needed libraries
library( dplyr )
library( tidyr )
library( ggplot2 )
library( openxlsx )
library( ggrepel )
library( here )

# load the data file
dat <- read.xlsx( 
  here( "sccj-faculty-salary-data.xlsx" ) 
  )

```

```{r data-prep}

# ----
# This section preps the data

# create year labels
label.years <- min( unique( dat$year ) ): max( unique( dat$year ) )


```


Faculty Salary
=====================================  

Column {.sidebar}
-----------------------------------------------------------------------

```{r}

            # make checkbox for rank
            checkboxGroupInput( inputId = "checkRank" ,
                                label = h3( "Faculty Rank" ), 
                                choices = list( "Assistant" = "Assistant", "Associate" = "Associate", "Full" = "Professor" ),
                                selected = "Professor" 
                                )

            # make checkbox for gender
            checkboxGroupInput( inputId = "checkSex" ,
                                label = h3( "Faculty Sex" ), 
                                choices = list( "Male" = "M", "Female" = "F" ),
                                selected = "F" 
                                )



```


Column
-----------------------------------------------------------------------

```{r}



renderPlot({
  
  ggplot(
    dat[ ( dat$rank %in% input$checkRank ) & ( dat$sex %in% input$checkSex ),],
    aes( x = year, y = rate, group = ID ) 
    ) +
    geom_line( color = "grey40" ) + 
    geom_point( color = "grey40" ) +
    facet_grid( rank ~ . , scales = "free_y", labeller = label_both, switch = "y" ) + 
    scale_y_continuous( label = scales::dollar ) +
    scale_x_continuous(
      breaks = label.years,
      label = as.character( label.years ) 
      ) + 
    geom_text_repel( aes( label = l.name ), 
                     point.size = 0.2, segment.curvature = -0.1, segment.ncp = 3, segment.angle = 20, max.overlaps = Inf ) +
    ggtitle( 
      paste( "ASU CCJ Faculty Salaries for Professors (", 
             as.character( head( label.years, 1 ) ), "to", as.character( tail( label.years, 1 ) ), ")", sep = " " ) ) +  
    theme_minimal()
  
  })

```

About
===================================== 

Row 
-------------------------------------

### About this Dashboard

The [State Press](https://www.statepress.com/article/2017/04/spinvestigative-salary-database) maintains a data base of salaries for all Arizona government employees. The data are available [here](https://www.statepress.com/article/2017/04/spinvestigative-salary-database). I have compiled the data for CCJ faculty and those data are used in the dashboard. For some cases there are no values reported. This is because the individual was not yet employed at ASU or they were not in the database (for reasons unknown to me).

Data from 2023 are pulled from [opengovpay](https://opengovpay.com/).

<br>

***Please*** report any needed corrections to the [Issues](https://github.com/jacobtnyoung/sccj-faculty-salary/issues/new) page. Thanks!


<style>

.chart-shim { overflow: auto; }

table{
   border-spacing:1px;
   margin-top:30px;
   margin-bottom:30px;
   margin-left: auto;
   margin-right: auto;
   align:center} 

td{ padding: 6px 10px 6px 10px } 

th{ text-align: left; } 

</style>
